Meta-analysis on diagnosis and sex in MSSM-Penn-Pitt and HBCC ACC/DLPFC

### 2020-07-31 individual-cohorts/meta-analysis.Rmd
fix contrasts for all conditions

# Control vs SCZ
```{r meta_analysis.SZ}
make_list <- function(mpp, hbcc, string) {
  list <- list(MPP = mpp %>%
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame,
               HBCC = hbcc %>% 
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame)
}

dlpfcList <- make_list(mpp_dlpfc, hbcc_dlpfc, string = "Control_vs_SCZ")
accList <- make_list(mpp_acc, hbcc_dsACC, string = "Control_vs_SCZ")

@@

# Control vs Other/SCZ
```{r meta_analysis.SCZOther}
make_list <- function(mpp, hbcc, string) {
  list <- list(MPP = mpp %>%
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame,
               HBCC = hbcc %>% 
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame)
}

dlpfcList <- make_list(mpp_dlpfc, hbcc_dlpfc, string = "Control_vs_OtherSCZ")
accList <- make_list(mpp_acc, hbcc_dsACC, string = "Control_vs_OtherSCZ")

@@

# Control vs Other
```{r meta_analysis.CTOther}
make_list <- function(mpp, hbcc, string) {
  list <- list(MPP = mpp %>%
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame,
               HBCC = hbcc %>% 
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame)
}

dlpfcList <- make_list(mpp_dlpfc, hbcc_dlpfc, string = "Control_vs_Other")
accList <- make_list(mpp_acc, hbcc_dsACC, string = "Control_vs_Other")

@@

# Other vs SCZ
```{r meta_analysis.OtherSCZ}
make_list <- function(mpp, hbcc, string) {
  list <- list(MPP = mpp %>%
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame,
               HBCC = hbcc %>% 
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame)
}

dlpfcList <- make_list(mpp_dlpfc, hbcc_dlpfc, string = "Other_vs_SCZ")
accList <- make_list(mpp_acc, hbcc_dsACC, string = "Other_vs_SCZ")

>>>>

# Control - Female vs Male
```{r meta_analysis.SZ}
make_list <- function(mpp, hbcc, string) {
  list <- list(MPP = mpp %>%
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame,
               HBCC = hbcc %>% 
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame)
}

dlpfcList <- make_list(mpp_dlpfc, hbcc_dlpfc, string = "Control_Female_vs_Control_Male")
accList <- make_list(mpp_acc, hbcc_dsACC, string = "Control_Female_vs_Control_Male")

@@

# SCZ - Female vs Male
```{r meta_analysis.SCZOther}
make_list <- function(mpp, hbcc, string) {
  list <- list(MPP = mpp %>%
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame,
               HBCC = hbcc %>% 
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame)
}

dlpfcList <- make_list(mpp_dlpfc, hbcc_dlpfc, string = "SCZ_Female_vs_SCZ_Male")
accList <- make_list(mpp_acc, hbcc_dsACC, string = "SCZ_Female_vs_SCZ_Male")

@@

#Other - Female vs Male
```{r meta_analysis.CTOther}
make_list <- function(mpp, hbcc, string) {
  list <- list(MPP = mpp %>%
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame,
               HBCC = hbcc %>% 
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame)
}

dlpfcList <- make_list(mpp_dlpfc, hbcc_dlpfc, string = "Other_Female_vs_Other_Male")
accList <- make_list(mpp_acc, hbcc_dsACC, string = "Other_Female_vs_Other_Male")

@@

# Female - Control vs Other/SCZ
```{r meta_analysis.OtherSCZ}
make_list <- function(mpp, hbcc, string) {
  list <- list(MPP = mpp %>%
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame,
               HBCC = hbcc %>% 
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame)
}

dlpfcList <- make_list(mpp_dlpfc, hbcc_dlpfc, string = "Control_Female_vs_Other_FemaleSCZ_Female")
accList <- make_list(mpp_acc, hbcc_dsACC, string = "Control_Female_vs_Other_FemaleSCZ_Female")

# Male - Control vs Other/SCZ
```{r meta_analysis.OtherSCZ}
make_list <- function(mpp, hbcc, string) {
  list <- list(MPP = mpp %>%
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame,
               HBCC = hbcc %>% 
                 unique() %>% 
                 dplyr::filter(Comparison == string) %>% 
                 as.data.frame)
}

dlpfcList <- make_list(mpp_dlpfc, hbcc_dlpfc, string = "Control_Male_vs_Other_MaleSCZ_Male")
accList <- make_list(mpp_acc, hbcc_dsACC, string = "Control_Male_vs_Other_MaleSCZ_Male")
